---
output: rmarkdown::github_document
---

# MACtools

Tools to Work with Media Access Control ('MAC') Addresses

## Description

A media access control address (MAC address) of a device is a unique identifier assigned to a network interface controller (NIC) for communications at the data link layer of a network segment. MAC addresses are used as a network address for most IEEE 802 network technologies, including Ethernet and Wi-Fi. In this context, MAC addresses are used in the medium access control protocol sublayer. Tools are provided to work with these 'MAC' addresses.

Ref: <https://github.com/hdm/mac-ages>

## What's Inside The Tin

The following functions are implemented:

- `mac_match_age`:	Lookup ages of MAC addresses
- `mac_match_registry`:	Lookup registry metadata of MAC addresses
- `mac_to_binary_string`:	Convert MAC address character vector to a binary string representation
- `rebuild_search_tries`:	Rebuild in-memory search tries
- `update_mac_age_db`:	Update MAC Address Age Database
- `update_registry_data`:	Update registry data

The following datasets are included:

- `mac_age_db`:	MAC Age Database
- `mac_registry_data`:	MAC Registry Data

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/MACtools")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(MACtools)
library(tidyverse)

# current verison
packageVersion("MACtools")

```

### Give it a go

```{r}
c(
  "2e:ab:a4:38:20:69", "70:26:5:19:23:25", "b8:e8:56:35:36:4", 
  "f4:f5:d8:df:67:44", "44:d9:e7:7a:9e:25", "f4:f5:d8:a7:94:66", 
  "a4:77:33:f2:50:30", "0:3e:e1:c3:9d:7a", "f0:23:b9:eb:42:4", 
  "c8:69:cd:28:5a:7d", "d4:85:64:74:49:de", "3c:7:54:52:fe:11"
) -> macs

mac_match_age(macs)

mac_match_registry(macs)
```